Combination of field and experimental data together with computational models reveal cognitive mechanisms behind cleaner fish behaviour

### 2022-01-06 manuscript_1.0/manuscript_1.0.Rmd
Fix issues with the size of figures in the formatted version

```{r post, fig.cap="Posterior distributions for parameter values $\\gamma$, $\\eta$ and the scaling constant. We show the kernel density estimates, below the mode (black point) and the 65\\% (light blue) and 95\\% (grey)  highest posterior density interval for the three paramteres. On the left (panels a, c and c) posterior distributions for a model with   all three parameters; while on the right (b and d) a model without negative reward. Panel f shows a measure of fit for both models, namely the distribution of pseudo-$R^2$ obtained from sampling the posterior distribution of parameter values.",out.width='95%',fig.height=9}
require(data.table)
library(coda)
library(ggplot2)
library(cowplot)
library(ggdist)
source(here("../R_files/posPlots.R"))
source(here("loadData.R"))
library("jsonlite")

@@

# NLables names for the three scenarios
labels.Scen<-c("both","gam","Nrew")
labelsPlot.Scen<-c("Full model","Future reward","Negative reward")

@@

panel.rsqr.all<-
  ggplot(data=loglikehoods.all[is.finite(lglikelihood)],
                  aes(y=model,x=Rsqrd,fill=model))+
  stat_halfeye(alpha=0.5,point_size=3)+
  theme_classic()+xlim(-0.5,0.3)+
  scale_fill_manual(values=c("#1b9e77","#d95f02","#7570b3"),
  name = "Model", labels = labelsPlot.Scen)+
  geom_vline(xintercept = 0,color="black",size=1)+
  theme(legend.position = c(.3, .80),legend.key.size = unit(0.4,'cm'),
        axis.text.y = element_blank())

plot_grid(nrow=3,align = "v",byrow = FALSE,
          # Full model - \gamma
          ggplot(data=MCMCdata1,aes(x=gamma)) + 
            stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.1$gamma))),
                         point_interval = mode_hdi, .width = c(.66, .95),point_size=3,
                         show.legend=FALSE) + 
            labs(title=labelsPlot.Scen[1],subtitle = expression(gamma),x="",y="")+
            theme_classic()+scale_fill_manual(values=c("gray85","skyblue","gray85")),
          # \eta
          ggplot(data=MCMCdata1,aes(x=negReward)) + 
            stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.1$negReward))),
                         point_interval = mode_hdi, .width = c(.66, .95),point_size=3,
                         show.legend=FALSE)+theme_classic()+
            scale_fill_manual(values=c("gray85","skyblue","gray85"))+
            labs(subtitle = expression(eta),x="",y="")+xlim(-5,5),
          # Scale Constant
          ggplot(data=MCMCdata1,aes(x=scaleConst)) + 
            stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.1$scaleConst))),
                         point_interval = mode_hdi, .width = c(.66, .95),point_size=3,
                         show.legend=FALSE)+
            theme_classic()+scale_fill_manual(values=c("skyblue","gray85"))+
          labs(subtitle = "Scalling const.",x="",y="")+xlim(-2,1500)+theme_classic(),
          # Future reward only model - \gamma
          ggplot(data=MCMCdata2,aes(x=gamma)) +
            stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.2$gamma))),
                         point_interval = mode_hdi, .width = c(.66, .95),point_size=3,
                         show.legend=FALSE) +
            scale_fill_manual(values=c("gray85","skyblue","gray85"))+
            labs(title=labelsPlot.Scen[2],subtitle = expression(gamma),x="",y="")+
            theme_classic(),
          # Scalling constant
          ggplot(data=MCMCdata2,aes(x=scaleConst)) +
            stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.2$scaleConst))),
                         point_interval = mode_hdi, .width = c(.66, .95),point_size=3,
                         show.legend=FALSE) +
            scale_fill_manual(values=c("gray85","skyblue","gray85"))+
            labs(subtitle = "Scalling const.",x="",y="")+
            theme_classic(),
          # Pseudo R^2
          panel.rsqr.all+labs(subtitle = expression(pseudo-R^2),x="",y=""),
          labels=c('a','b','c','d','e')
)

@@

```{r pred, fig.cap="Observed and predicted probability of choosing a visitor. Left-hand side panel: color contour shows the prediction of the learning model using the mode of the posterior distributions of parameters recovered by the statistical analysis. Dots show the frequency of visitor choices for the 12 locations, as well as the corresponding relative cleaner abundance (x axis) and frequency of visitors leaving the station (y axis). Right-hand side panels: scatter plot of the observed and predicted probabilities of choosing a visitor for 12 locations. Line correspond to a perfect match between observed and predicted probabilities. Pseudo $R^2$ shown in the lower right corner corresponds to the fit of a model parameterized with the mode of the posterior distributions. Upper panels show prediction from a model including future and negative reward, lower panels froma  model with only future reward.",out.width='95%',fig.height=8}

@@

```{=tex}
\beginsupplement
```
```{r nogamma, fig.cap="Observed and predicted probability of choosing a visitor for a model without future rewards. Left-hand side panel: color contour shows the prediction of the learning model using the mode of the posterior distributions of parameters recovered by the statistical analysis. Dots show the frequency of visitor choices for the 12 locations, as well as the corresponding relative cleaner abundance (x axis) and frequency of visitors leaving the station (y axis). Right-hand side panel: scatter plot of the observed and predicted probabilities of choosing a visitor for 12 locations. Line correspond to a perfect match between observed and predicted probabilities.",fig.pos = 'H', out.extra = "",out.width='95%',fig.height=8}

>>>>

```{r post, fig.cap="Posterior distributions for parameter values $\\gamma$, $\\eta$ and the scaling constant. We show the kernel density estimates, below the mode (black point) and the 65\\% (light blue) and 95\\% (grey)  highest posterior density interval for the three paramteres. On the left (panels a, c and c) posterior distributions for a model with   all three parameters; while on the right (b and d) a model without negative reward. Panel f shows a measure of fit for both models, namely the distribution of pseudo-$R^2$ obtained from sampling the posterior distribution of parameter values.",out.width='100%',fig.height=7}
library(data.table)
library(coda)
library(ggplot2)
library(cowplot)
library(ggdist)
source(here("../R_files/posPlots.R"))
source(here("loadData.R"))
library("jsonlite")

@@

# NLables names for the three scenarios
labels.Scen<-c("both","gam","Nrew")
labelsPlot.Scen<-c("Full \n model","Future \n reward","Negative \n reward")

@@

panel.rsqr.all<-
  ggplot(data=loglikehoods.all[is.finite(lglikelihood)],
                  aes(y=model,x=Rsqrd,fill=model))+
  stat_halfeye(alpha=0.5,point_size=3)+
  theme_classic()+xlim(-0.6,0.2)+
  scale_fill_manual(values=c("#1b9e77","#d95f02","#7570b3"),
  name = "Model", labels = labelsPlot.Scen)+
  geom_vline(xintercept = 0,color="black",size=1)+
  theme(legend.position = c(.3, .75),legend.key.size = unit(0.25,'cm'),
        axis.text.y = element_blank())

plot_grid(nrow=3,align = "v",byrow = FALSE,
          # Full model - \gamma
          ggplot(data=MCMCdata1,aes(x=gamma)) + 
            stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.1$gamma))),
                         point_interval = mode_hdi, .width = c(.66, .95),point_size=3,
                         show.legend=FALSE) + 
            labs(title=labelsPlot.Scen[1],subtitle = expression(gamma),x="",y="")+
            theme_classic()+scale_fill_manual(values=c("gray85","skyblue","gray85"))+
            theme(plot.margin = unit(rep(0.5,4), "lines")),
          # \eta
          ggplot(data=MCMCdata1,aes(x=negReward)) + 
            stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.1$negReward))),
                         point_interval = mode_hdi, .width = c(.66, .95),point_size=3,
                         show.legend=FALSE)+theme_classic()+
            scale_fill_manual(values=c("gray85","skyblue","gray85"))+
            labs(subtitle = expression(eta),x="",y="")+xlim(-5,5)+
            theme(plot.margin = unit(rep(0.5,4), "lines")),
          # Scale Constant
          ggplot(data=MCMCdata1,aes(x=scaleConst)) + 
            stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.1$scaleConst))),
                         point_interval = mode_hdi, .width = c(.66, .95),point_size=3,
                         show.legend=FALSE)+
            theme_classic()+scale_fill_manual(values=c("skyblue","gray85"))+
          labs(subtitle = "Scalling const.",x="",y="")+xlim(-2,1500)+theme_classic()+
          theme(plot.margin = unit(rep(0.5,4), "lines")),
          # Future reward only model - \gamma
          ggplot(data=MCMCdata2,aes(x=gamma)) +
            stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.2$gamma))),
                         point_interval = mode_hdi, .width = c(.66, .95),point_size=3,
                         show.legend=FALSE) +
            scale_fill_manual(values=c("gray85","skyblue","gray85"))+
            labs(title=labelsPlot.Scen[2],subtitle = expression(gamma),x="",y="")+
            theme_classic()+theme(plot.margin = unit(rep(0.5,4), "lines")),
          # Scalling constant
          ggplot(data=MCMCdata2,aes(x=scaleConst)) +
            stat_halfeye(aes(fill=stat(cut(x,breaks = cuts.2$scaleConst))),
                         point_interval = mode_hdi, .width = c(.66, .95),point_size=3,
                         show.legend=FALSE) +
            scale_fill_manual(values=c("gray85","skyblue","gray85"))+
            labs(subtitle = "Scalling const.",x="",y="")+
            theme_classic()+theme(plot.margin = unit(rep(0.5,4), "lines")),
          # Pseudo R^2
          panel.rsqr.all+labs(subtitle = expression(pseudo-R^2),x="",y=""),
          labels=c('a','b','c','d','e')
)

@@

```{r pred, fig.cap="Observed and predicted probability of choosing a visitor. Left-hand side panel: color contour shows the prediction of the learning model using the mode of the posterior distributions of parameters recovered by the statistical analysis. Dots show the frequency of visitor choices for the 12 locations, as well as the corresponding relative cleaner abundance (x axis) and frequency of visitors leaving the station (y axis). Right-hand side panels: scatter plot of the observed and predicted probabilities of choosing a visitor for 12 locations. Line correspond to a perfect match between observed and predicted probabilities. Pseudo $R^2$ shown in the lower right corner corresponds to the fit of a model parameterized with the mode of the posterior distributions. Upper panels show prediction from a model including future and negative reward, lower panels froma  model with only future reward.",out.width='100%',fig.height=6}

@@

```{=tex}
\beginsupplement
```
```{r nogamma, fig.cap="Observed and predicted probability of choosing a visitor for a model without future rewards. Left-hand side panel: color contour shows the prediction of the learning model using the mode of the posterior distributions of parameters recovered by the statistical analysis. Dots show the frequency of visitor choices for the 12 locations, as well as the corresponding relative cleaner abundance (x axis) and frequency of visitors leaving the station (y axis). Right-hand side panel: scatter plot of the observed and predicted probabilities of choosing a visitor for 12 locations. Line correspond to a perfect match between observed and predicted probabilities.",fig.pos = 'H', out.extra = "",out.width='95%',fig.height=4}

### 2022-01-06 manuscript_1.0/manuscript_1.0.tex
Fix issues with the size of figures in the formatted version

{\centering \includegraphics[width=0.95\linewidth]{manuscript_1.0_files/figure-latex/post-1}

@@

{\centering \includegraphics[width=0.95\linewidth]{manuscript_1.0_files/figure-latex/pred-1}

>>>>

{\centering \includegraphics[width=1\linewidth]{manuscript_1.0_files/figure-latex/post-1}

@@

{\centering \includegraphics[width=1\linewidth]{manuscript_1.0_files/figure-latex/pred-1}
